%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header
\documentclass[11pt]{report}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{fullpage}
\usepackage{amssymb}
\usepackage{enumitem}

\setlength{\parindent}{0cm}


\begin{document}
\title{Class Test: Syntax Test}
\subsubsection*{EMAT10007 -- Introduction to Computer Programming}
\subsection*{\Large Syntax Test - Checklist}

The Syntax Test on Friday 1st November will cover the topics listed below. Recommended preparation is to answer all the example questions given last week and to make sure you understand everything on this list.\\

Don't forget to use the Support Forum on Blackboard if you have any questions.

\begin{enumerate}[leftmargin=*]
    \item Operators ({\tt +}, {\tt -}, {\tt *}, {\tt /}, {\tt \%}, {\tt //}, etc)
    \item Variable assignment, including;
    \begin{itemize}
        \item different assignment operators,
        \item assignment over multiple lines,
        \item rewriting variables,
        \item chaining assignment.
    \end{itemize}
    \item Types ({\tt int}, {\tt float}, {\tt string}, {\tt complex}, {\tt boolean}), including;
    \begin{itemize}
        \item identify the type of a variable,
        \item implicit type casting,
        \item how to explicitly type cast.
    \end{itemize}
    \item Data Structures (lists, sets, tuples and dictionaries), including;
    \begin{itemize}
        \item key characteristics of each data structure,
        \item how to return values from data structures,
        \item how to add values to data structures,
        \item indexing data structures.
    \end{itemize}
    \item Conditionals ({\tt if}, {\tt else}, {\tt elif}), including;
    \begin{itemize}
        \item boolean terms: {\tt not}, {\tt and}, {\tt or}, {\tt in}, {\tt ==}, {\tt !=}, etc,
        \item conditional statement structure and precedence
    \end{itemize}
    \item Loops ({\tt for}, {\tt while}), including;
    \begin{itemize}
        \item structure of a loop (indentation, colon, condition has to be true),
        \item how to loop through a list,
        \item how to loop through a string,
        \item how to loop through a dictionary ({\tt keys()}, {\tt values()}, {\tt items()}).
    \end{itemize}
    \item Predicting behaviour, including;
    \begin{itemize}
        \item predicting the output from a code snippet,
        \item filling in the blanks in a code snippet sop that it produces the given output.
    \end{itemize}
    \item Errors, including;
    \begin{itemize}
        \item Identify errors/bugs in code,
        \item predict error type i.e. the \textbf{why} of an error:
            \begin{itemize}
                \item {\tt SyntaxError} - usually typos such as misspelling of keywords, missing colons and brackets, incorrect indentation, etc.
                \item {\tt NameError} - when a variable or function is being used without being previously defined.
                \item {\tt TypeError} - when an operation or function is applied to an variable of an inappropriate type.
            \end{itemize}
    \end{itemize}
\end{enumerate}






\end{document}